\documentclass[addpoints,12pt]{exam}
\usepackage{fullpage,xypic,mathrsfs}
\usepackage{amsmath, amsthm, amssymb, latexsym}
\usepackage{enumerate}
\usepackage{hyperref}
%\usepackage[sans]{dsfont}

\usepackage[margin=0.7in]{geometry}

\usepackage{bm}
\newcommand{\mbf}[1]{\boldsymbol{\mathbf{#1}}}

\title{\vspace{-1in} MATH 362---Work Sheet 04}
\date{Due on Tuesday (!) February 16, 2021}
\author{Dr.~Justin M. Curry}


%\input{shortcuts}

\begin{document}
\maketitle

% \begin{center}
% \fbox{\fbox{\parbox{6in}{\centering
% \textbf{Open Book. Open Notes. Open Friends.}}}}
% \end{center}
% \vspace{0.2in}
\makebox[.9\textwidth]{Name:\enspace\hrulefill}
% % \vspace{0.2in}
% % \makebox[\textwidth]{Instructor’s name: Dr. Justin Curry}

\begin{questions}
\question[4]
An urn contains 15 red balls, 20 green balls and 12 yellow balls. Consider the experiment where we draw two balls without replacement. Consider the event $A$ where exactly one red ball {\em or} one yellow ball is drawn.
\noaddpoints
\begin{parts}
\part[2] Decompose the event $A$ into three mutually exclusive events and use this decomposition to compute the probability of $A$.

\vspace{1.8in}

\part[2] Notice that $A$ is the union of the events
\[
  R=\{\text{exactly one red ball is drawn}\} \cup Y=\{\text{exactly one yellow ball is drawn}\}
\]
Why are these events not disjoint? Compute $P(A)$ using the formula $$P(A)=P(R)+P(Y)-P(R\cap Y).$$

\vspace{1.2in}

\end{parts}
\addpoints

\question[2] Suppose I deal a regular 52 card deck to 4 people, by giving each person 13 cards uniformly at random. What's the probability that each person gets exactly one Ace?

\vspace{2in}

\question[2] An urn contains 10 red balls, 7 green balls and 3 yellow balls. Draw 5 balls. 
\noaddpoints
\begin{parts}
\part[1]
What's the probability that you draw 2 red, 2 green and 1 yellow?

\part[1]
Same experiment as above. What's the probability that you draw 2 red, 1 green and 2 yellow?
\end{parts}
\addpoints

\vspace{1.5in}


\question[1] How many ways are there of rearranging the letters in \texttt{WAAHOOO}?

\vspace{1.2in}

\question[1] 6 people in a house are charged with completing one of three different chores: two people sweep, two people clean bathrooms, and two people do the dishes. How many ways are there of assigning people to do these tasks?

\vspace{2in}

\question[1] How many ways are there of splitting 6 people into 3 pairs? 
\end{questions}

\end{document}
