\documentclass[addpoints,12pt]{exam}
\usepackage{fullpage,xypic,mathrsfs}
\usepackage{amsmath, amsthm, amssymb, latexsym}
\usepackage{enumerate}
\usepackage{hyperref}
%\usepackage[sans]{dsfont}

\usepackage{graphicx}

\usepackage[margin=0.7in]{geometry}

\usepackage{bm}
\newcommand{\mbf}[1]{\boldsymbol{\mathbf{#1}}}

\title{\vspace{-1in} MATH 362---Work Sheet 16}
\date{NOT DUE B/C MIDTERM 2}
\author{Dr.~Justin M. Curry}


%\input{shortcuts}

\begin{document}
\maketitle

% \begin{center}
% \fbox{\fbox{\parbox{6in}{\centering
% \textbf{Open Book. Open Notes. Open Friends.}}}}
% \end{center}
% \vspace{0.2in}
\makebox[.9\textwidth]{Name:\enspace\hrulefill}
% % \vspace{0.2in}
% % \makebox[\textwidth]{Instructor’s name: Dr. Justin Curry}





\begin{questions}

\question Suppose an urn has 3 red balls and 1 green ball. Suppose I make draws with replacement until I get the green ball. Call this number of draws the random variable $D$.
\noaddpoints
\begin{parts}

\part What's the probability that $D=1$?
\vspace{1in}
\part What's the probability that $D=3$?
\vspace{1in}
\part What's the probability that $D>3$?
\vspace{1.5in}
\part What's the probability that $D>7$ \emph{given} the information that $D>4$?
\vspace{1.5in}
\part What's mean and standard deviation of $D$?
\vspace{1.5in}
\end{parts}
\addpoints

\question I like to compete in apple bobbing\footnote{\url{https://en.wikipedia.org/wiki/Apple_bobbing}} competititons. Everytime I dunk my head underwater to get an apple, I have a probability of $1/5$ of successfully retrieving the apple with my teeth. I win the competition after successfully retrieving 3 apples. 

 \noaddpoints
\begin{parts}
\part Name the probability distribution that governs the number of times I need to dunk my head to get 3 apples.
\vspace{1in}
\part Compute the probability that I retrieve my third apple on the 7th attempt.
\vspace{1.2in}

\part Compute the mean and standard deviation of the number of times I need to bob for apples to get 3 apples.
\vspace{1.5in}
\end{parts}
\addpoints

\question Suppose $S_2=X_1 + X_2$ represents the sum of two rolls of a 6 sided die. Compute the mean and standard deviation of $S_2$.

\vspace{1.3in}

\newpage
\question \emph{The Collector's Problem---This is a challenging problem that we will discuss in class.}
When I was young, I loved the power rangers. My favorite cereal started including small action figures of the following five power rangers: The Red Ranger, The Pink Ranger, The Blue Ranger, the Yellow Ranger and the Black Ranger. Assuming there is a uniform distribution of the 5 rangers across cereal boxes. How many boxes of cereal should I expect to buy before collecting all five?

\vspace{3in}



\question Suppose only 1\% of the population is over 6 feet 3 inches tall. Out of a randomly selected group of 200 people, what's the probability that at least 4 of them are over 6'3".

\vspace{1.5in}

\question How many raisins must cookies contain on average for the chance of the of a cookie containing at least one raisin to be at least 99\%?



\end{questions}

\end{document}
