\documentclass[addpoints,12pt]{exam}
\usepackage{fullpage,xypic,mathrsfs}
\usepackage{amsmath, amsthm, amssymb, latexsym}
\usepackage{enumerate}
\usepackage{hyperref}
%\usepackage[sans]{dsfont}

\usepackage[margin=0.7in]{geometry}

\usepackage{bm}
\newcommand{\mbf}[1]{\boldsymbol{\mathbf{#1}}}

\title{\vspace{-1in} MATH 362---Work Sheet 05}
\date{Due on Saturday February 20th, 2021}
\author{Dr.~Justin M. Curry}


%\input{shortcuts}

\begin{document}
\maketitle

% \begin{center}
% \fbox{\fbox{\parbox{6in}{\centering
% \textbf{Open Book. Open Notes. Open Friends.}}}}
% \end{center}
% \vspace{0.2in}
\makebox[.9\textwidth]{Name:\enspace\hrulefill}
% % \vspace{0.2in}
% % \makebox[\textwidth]{Instructor’s name: Dr. Justin Curry}

\begin{questions}
\question[2]
You are dealt two cards, one at a time, from a standard 52 card deck.
\noaddpoints
\begin{parts}
\part[1] What's the probability that the second card is black?

\vspace{1in}

\part[1] What's the probability that the second card is black, given that the first card is black?

\vspace{1in}
\end{parts}
\addpoints


\question[4]
\emph{The Two Queens Problem:} In Texas Hold-em, every player is dealt two cards from a standard 52 card deck.
\noaddpoints
\begin{parts}
\part[1] What's the probability of being dealt two Queens?

\vspace{1in}

\part[1] What's the probability of having two Queens assuming you know you have at least one queen?
\vspace{1in}

\part[1] What's the probability of having two Queens assuming you know you have the Queen of Hearts?
\vspace{1in}

\part[1] How do these probabilities compare?
\vspace{1in}

\end{parts}
\addpoints

\question[2]
Describe \emph{The Monty Hall Problem}. Should you switch doors?

\vspace{2in}

\question[3]
\emph{Electrical Components:} Suppose there are two electrical components in a device. The chance that the first component fails is 10\%. If the first component fails then the chance that the second component fails is 20\%. If the first component works, the chance the second component fails is only 5\%.
\noaddpoints
\begin{parts}
\part[1] What's the probability at least one component works.

\vspace{1in}

\part[1] What's the probability exactly one component works?
\vspace{1in}

\part[1] What's the probability the second component works?
\vspace{1in}

\end{parts}
\addpoints


\question[1] Suppose $P(\text{snow today})=40\%$ and $P(\text{snow tomorrow})=50\%$ and $P(\text{snow today and tomorrow})=30\%$, what is $P(\text{snow tomorrow}\mid \text{snow today})=$?

\vspace{1.2in}

\question[3]
\emph{Two Urns:} One urn contains 2 black and 3 white balls. The other urn contains 4 black balls and 3 white balls. An urn is chosen uniformly at random and a ball is chosen uniformly at random from that urn.
\noaddpoints
\begin{parts}
\part[1] Draw a tree diagram illustrating the possible outcomes of this experiment.

\vspace{2in}

\part[1] Assign probabilities and conditional probabilities to branches in the tree.
\vspace{1in}

\part[1] Calculate the total probability that the urn is black.
\vspace{1in}

\end{parts}
\addpoints

\question[2] A light bulb company has factories in two cities. The factory in city $A$ produces two thirds of the company's light bulbs. The remainder are produced in city $B$, and of these, 1\% are defective. Among all bulbs manufactured by the company, what proportion are not defective and made in city $B$?

\vspace{2in}

\question[4]
\emph{True and False:} In a particular population of men and women. 92\% of women are right handed and 88\% of men are right handed. Indicate whether each of the following statements are (i) true, (ii) false, or (iii) can't be determined using the information given.
\noaddpoints
\begin{parts}
\part[1] The overall proportion of right handers in the population is exactly 90\%.

\vspace{1in}

\part[1] The overall proportion of right handers in the population is between 88\% and 92\%.
\vspace{1in}

\part[1] If the sex ratio in the population is 1-to-1 then Part A is true.
\vspace{1in}

\part[1] If Part A is true, then the sex ratio is 1-to-1.
\vspace{1in}


\end{parts}
\addpoints
\end{questions}

\end{document}
