\documentclass[addpoints,12pt]{exam}
\usepackage{fullpage,xypic,mathrsfs}
\usepackage{amsmath, amsthm, amssymb, latexsym}
\usepackage{enumerate}
\usepackage{hyperref}
%\usepackage[sans]{dsfont}

\usepackage{graphicx}

\usepackage[margin=0.7in]{geometry}

\usepackage{bm}
\newcommand{\mbf}[1]{\boldsymbol{\mathbf{#1}}}

\title{\vspace{-1in} MATH 362---Work Sheet 08}
\date{Due on Sunday, February 28th, 2021}
\author{Dr.~Justin M. Curry}


%\input{shortcuts}

\begin{document}
\maketitle

% \begin{center}
% \fbox{\fbox{\parbox{6in}{\centering
% \textbf{Open Book. Open Notes. Open Friends.}}}}
% \end{center}
% \vspace{0.2in}
\makebox[.9\textwidth]{Name:\enspace\hrulefill}
% % \vspace{0.2in}
% % \makebox[\textwidth]{Instructor’s name: Dr. Justin Curry}

\begin{questions}
\question[1] A flush in poker is a five card hand where each card has the same suit. What's the probability of a flush?

\vspace{1in}

\question[1] How many ways are there to choose 12 donuts from the 22 varieties of donuts at a donut shop?

\vspace{1in}

\question[2] How many ways can you give 10 cookies to 4 distinct people, assuming each person gets at least 1 cookie?

\vspace{1in}

\question[2] Assume that $P(\text{Woman}\mid \text{Yoga Person})=75\%$. What's the probability that a 10 person yoga class has at least 8 women in it?

\vspace{1.2in}

\question[6] I can land a heel flip \url{https://youtu.be/2A2P_tcqaZ8} once out of every 42 attempts.
\noaddpoints
\begin{parts}
\part[2] What's the probability that I'll land a heel flip in the first 3 attempts?

\vspace{1.2in}
\newpage
\part[2] What's the probability that I'll land a heel flip after 5 tries?

\vspace{1.2in}

\part[2] How many times should I try to do a heel flip to make it more than 50\% likely that I'll land at least one heel flip?

\vspace{1.5in}
\end{parts}
\addpoints

\question[2] Challenge Problem: How many 5-digit numbers have their digits in non-decreasing order? Examples include: 55555 and 12345. Non-examples include 12343. Hint: This is a stars and bars problem.

\end{questions}

\end{document}
