\documentclass[11pt,reqno]{amsproc}
\usepackage{termcal}
%\title{Research Statement --- Justin M. Curry\vspace{-1in}}

\setlength{\parskip}{0.45\baselineskip}

\usepackage{amsmath,mathrsfs}
\usepackage{amssymb,latexsym}
%\usepackage{eulervm}

\usepackage{graphicx}
\usepackage{nicefrac}
\usepackage[usenames,dvipsnames]{color}
\usepackage[all]{xy}
\usepackage{pb-diagram,pb-xy}
%\usepackage[margin=1in,headheight=35pt,footskip=.3in]{geometry}
\usepackage[margin=0.7in]{geometry}
%\usepackage{fullpage}

\usepackage{hyperref}
\hypersetup
{
    colorlinks,	%
    citecolor=Gray,%
    filecolor=Gray,%
    linkcolor=Gray,%
    urlcolor=Gray
}

\usepackage{mdframed}
% \usepackage{tikz}

\mdfsetup{skipabove=\topskip,skipbelow=\topskip}



\input{shortcuts}

\usepackage{wrapfig}

\newcommand{\uline}{\underline}

\renewcommand{\refname}{\normalfont\selectfont\normalsize {\large \color{Gray}{references}}}

\renewcommand{\refname}{\normalfont\selectfont\normalsize {\large \color{Gray}{references}}}

\newcommand{\MWFClass}{%
\calday[Monday]{\classday} % Monday
\skipday % Tuesday (no class)
\calday[Wednesday]{\classday} % Wednesday
\skipday % Thursday (no class)
\calday[Friday]{\classday} % Friday
\skipday\skipday % weekend (no class)
}

\newcommand{\MWClass}{%
\calday[Monday]{\classday} % Monday
\skipday % Tuesday (no class)
\calday[Wednesday]{\classday} % Wednesday
\skipday % Thursday (no class)
%\calday[Friday]{\classday} % Friday
\skipday % Friday no class
\skipday\skipday % weekend (no class)
}

\newcommand{\TuThuClass}{%
\skipday % Monday (no class)
\calday[Tuesday]{\classday} % Tuesday
\skipday % Wednesday (no class)
\calday[Thursday]{\classday} % Wednesday
\skipday % Friday no class
\skipday\skipday % weekend (no class)
}

\newcommand{\Holiday}[2]{%
\options{#1}{\noclassday}
\caltext{#1}{#2}
}

\renewcommand{\calprintdate}{\textbf{\monthname\ \ordinaldate}}
\renewcommand{\calprintclass}{Lecture \theclassnum}

\begin{document}
\pagenumbering{gobble}
% \thispagestyle{fancy}
\begin{center}
	{\Large \color{Black}{AMAT 362---Probability for Statistics---Spring 2021 Syllabus}}
	\noindent\rule{\textwidth}{0.1pt}

	\textbf{Instructor:} Prof.~Justin M.~Curry \quad \textbf{Office:} ES 120C \quad \textbf{Email:} \url{jmcurry@albany.edu}
\end{center}

\noindent\textbf{Pre-Requisites:} Calculus of Several Variables (AMAT 214) and Introduction to Proofs (AMAT 299).

\noindent\textbf{Lecture Place and Times:} \emph{ONLINE} on \emph{MW 11:40-1:00pm}

\noindent\textbf{Office Hours Place and Times:} By appointment with Brendan Mallery \url{bmallery@albany.edu} or me.

\noindent\textbf{Course Texts:} The following texts are recommended:
\begin{itemize}
  \item \emph{Introduction to Probability} by Anderson, Sepp\"{a}l\"{a}inen, Valk\'{o} [ASV].
  \item \emph{Introduction to Probability} by Grinstead and Snell [GS];
  \item \emph{Probability} by Pittman [Pit];
  \item \emph{Introduction to Probability, 2nd edition} Bertsekas and Tsitsiklis [BT]
\end{itemize}

\noindent\textbf{Course Topics:}
This course is meant to serve as a calculus-based introduction to probability that provides a foundation for statistics as covered in AMAT 363.
Additionally, this course is meant to serve as preparation for the \emph{Society of Actuaries} Exam P. The topics for the P exam are listed below, but I will follow my own selection of topics and spend more or less time focusing on topics that I think are important.

\begin{enumerate}
	\item General Probability: set theory, Venn diagrams, sample space and events; definition of probability measure, basic axioms; addition and multiplication rules; independence versus mutually exclusive events; calculation of conditional probabilities; combinatorics; Bayes' theorem and law of total probability.
	\item Univariate Random Variables: discrete and continuous univariate random variables (RVs) including binomial, negative binomial, geometric, hypergeometric, Poisson, uniform, exponential, gamma, normal, mixed distributions and their applications; PDFs and CDFs of these RVs; expectation/mean, mode, median, percentile and higher moments; variance, standard deviation, coefficient of variation; probability and moment generating functions; sums of independent RVs, such as Poisson and Normal; transforms.
	\item  Multivariate Random Variables: joint probability functions (PFs), PDFs, CDFs; conditional and marginal PFs, PDFs, CDFs and moments for these; covariance and correlation; transforms of multivariate RVs; probabilities and moments for linear combinations of RVs; central limit theorem.
\end{enumerate}

\noindent\textbf{Grading Schema:}

\begin{itemize}
	\item $45 \%$ Lecture Worksheets
	\item $20 \%$ Final Exam
	\item $15 \%$ Exam 1
	\item $15 \%$ Exam 2
  \item $5\%$ Participation and Attendance
\end{itemize}

\noindent\textbf{Attendance and Missed Work Policy:}
Attendance is required unless a reasonable excuse is provided to the instructor via email. Worksheets corresponding to lectures 1-8 will be handed in as a packet before the first exam. Worksheets corresponding to lectures 9-16 will be handed in before the second exam. Worksheets corresponding to lectures 17-24 must be handed in before the final exam.

\noindent\textbf{Academic Dishonesty Policy:}

\begin{center}
\fbox{\fbox{\parbox{6.5in}{\centering
\emph{Use of Chegg.com and similar websites is strictly prohibited. Students who post questions from exams or worksheets on online forums such as Chegg will get an automatic 5\% subtracted from their overall grade for the first question posted. A 10\% subtraction will occur for the second posted question and an automatic failing grade will be given on the third offense.}

\textbf{THREE STRIKES AND YOU'RE OUT!}}}}
\end{center}



\newpage

\begin{center}


\textbf{The final exam will occur remotely between Wednesday, May 12, 2021 and Saturday, May 15, 2021.}

The format of the exams are still to be determined.

\begin{calendar}{2/01/2021}{15} % Put date of Monday of first week of classes and number of weeks
\setlength\calboxdepth{.25in}
\setlength\calwidth{\textwidth}
\MWClass




% schedule
%\caltexton{1}{$\heartsuit$\textit{NO ClASS---MLK DAY}$\heartsuit$}
% \caltexton{1}{L1:Admin + \S 1.1}
% \caltextnext{L2: \S 1.2}
% \caltextnext{L3: \S 1.3, 1.4}
% \caltextnext{L4: \S 1.4, 1.5}
% \caltextnext{L5: \S 2.1}
% \caltextnext{\S 2.2}
% \caltextnext{\S 2.3}
% \caltextnext{\S 2.4}
% \caltextnext{\S 2.5}
% \caltextnext{\S 3.1}
% \caltextnext{\S 3.2}
% \caltextnext{\S 3.3}
% \caltextnext{\S 3.4}
% \caltextnext{\S 3.5}
% \caltextnext{\S 4.1 - not on M1}
% \caltextnext{Review for Midterm 1}
% \caltextnext{}%Midterm
% \caltextnext{\S 4.2}
% \caltextnext{\S 4.3}
% \caltextnext{\S 4.4}
% \caltextnext{\S 4.5}
% \caltextnext{\S 4.6}
% \caltextnext{\S 5.2}
% \caltextnext{}%Spring Break
% \caltextnext{}%Spring Break
% \caltextnext{}%Spring Break
% \caltextnext{\S 6.1}
% \caltextnext{\S 6.2}
% \caltextnext{\S 6.3}
% \caltextnext{\S 6.4}
% \caltextnext{\S 7.1}
% %\caltextnext{\S 7.2}
% \caltextnext{\S 8.1}
% \caltextnext{\S 8.2}
% \caltextnext{\S 8.3}
% \caltextnext{\S 8.4}
% \caltextnext{\S 8.5 or catch-up}
% \caltextnext{Review for Midterm 2}
% \caltextnext{}%Midterm
% \caltextnext{\S 9.1}
% \caltextnext{\S 9.2/9.3}
% \caltextnext{\S 10.1}
% \caltextnext{\S 10.2}
% \caltextnext{\S 10.3}
% \caltextnext{\S 10.4}
% \caltextnext{Final Review Lecture}
% \caltextnext{[dGS] \S 5.2}
% \caltextnext{[dGS] \S 5.3}

%Exams
%\caltext{3/1/2021}{$\spadesuit$\textbf{Midterm 1 Answers}$\spadesuit$}
%\caltext{4/17/2020}{$\spadesuit$\textbf{Midterm 2}$\spadesuit$}
% \caltext{3/1/2018}{$\clubsuit$\textbf{Quiz 3}$\clubsuit$}

% \caltext{3/8/2018}{$\spadesuit$\textbf{MIDTERM}$\spadesuit$}

% \caltext{3/29/2018}{$\clubsuit$\textbf{Quiz 4}$\clubsuit$}
% \caltext{4/12/2018}{$\clubsuit$\textbf{Quiz 5}$\clubsuit$}
% \caltext{4/26/2018}{$\clubsuit$\textbf{Quiz 6}$\clubsuit$}

% Holidays
\Holiday{3/1/2021}{$\spadesuit$\textbf{Midterm 1}$\spadesuit$}
\Holiday{3/3/2021}{$\heartsuit$\textit{NO ClASS}$\heartsuit$}
\Holiday{4/5/2021}{$\spadesuit$\textbf{Midterm 2}$\spadesuit$}
% \Holiday{3/16/2020}{$\heartsuit$\textit{SPRING BREAK}$\heartsuit$}
% \Holiday{3/18/2020}{$\heartsuit$\textit{SPRING BREAK}$\heartsuit$}
%\Holiday{3/20/2020}{$\heartsuit$\textit{SPRING BREAK}$\heartsuit$}
\Holiday{5/10/2021}{$\spadesuit$\textbf{Final Review}$\spadesuit$}
\Holiday{5/12/2021}{$\heartsuit$\textit{NO MORE CLASSES}$\heartsuit$}
%\Holiday{5/8/2020}{$\heartsuit$\textit{NO MORE CLASSES}$\heartsuit$}
% \options{3/13/2018}{\noclassday}
% \options{3/13/2018}{\noclassday}
% \options{5/10/2018}{\noclassday}

\end{calendar}

\textbf{The final exam will occur remotely between Wednesday, May 12, 2021 and Saturday, May 15, 2021.}

\end{center}

\end{document}
